---
params:
    dynamictitle: "mytitledefinedintheparamslistofrender"
title: "`r params$dynamictitle`"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  html_document2:
    css: "../templates/html_template.css"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
      smooth_scroll: FALSE
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
---
  
```{r general_options, echo = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  size = 'small',
  
  tab.cap.pre = "Table ",
  tab.cap.sep = ". ",
  tab.cap.style ='Table Caption',
  
  fig.cap.style = "Caption label",
  fig.cap.pre = "Fig. ", 
  fig.cap.sep = ". ",
  
  fig.width   = 8,
  fig.height  = 4.5
)

knit_hooks$set(
  inline = function(x) {
    prettyNum(x, big.mark = "")
  }
)
```

```{r OutputTables, echo = FALSE}
out_dt = function(data, name) {
  datatable(data, 
            rownames = FALSE, 
            filter = "bottom", 
            extensions = "Buttons", 
            options = 
              list(dom = "Bfrtip", 
                   buttons = list(
                     list(
                       extend = "csv", 
                       filename = name
                     )
                   )
              )
  )
}
```

## Abstract

This dataset corresponds to the latest version of the best scientific estimates of annual catches in live-weight equivalent for the 16 IOTC species, aggregated by year, IOTC statistical area and fishing fleet, and fully disaggregated by species and fishing gear. Data are reported by calendar year and extend back to the 1950s, when industrial longlining started in the Indian Ocean.

The data originate from the IOTC Contracting Parties and Cooperating Non-Contracting Parties ([CPCs]((https://iotc.org/about-iotc/structure-commission) )) as per the IOTC data requirements (Resolution [15/02](https://www.iotc.org/cmm/resolution-1502-mandatory-statistical-reporting-requirements-iotc-contracting-parties-and)). They are submitted annually, mostly using IOTC Form [1RC](https://data.iotc.org/reference/latest/forms/#Form_1RC), and curated by the Secretariat for dissemination prior to IOTC Working Parties and other scientific data users.

The breakdown by species or gear is performed using additional sources of information available to the Secretariat, such as statistical publications, fishery bulletins, and other historical or proxy data. In some cases, the Secretariat may re-estimate the species or gear composition for strata affected by known data collection or reporting issues. These re-estimations are made in agreement with the IOTC Scientific Committee and may be revised in future updates.

## Global attributes

- **Title**: Best scientific estimates of retained catch by IOTC species, gear and vessel flag reporting country for 1950-2024
- **Summary**: Curated dataset providing detailed information on the tuna catches in the Indian Ocean
- **Context of development**: Management of tuna and tuna-like species under IOTC mandate
- **Data origin**: Retained catch data collected on land or at sea by national institutions and the fishing industry, with some data having been previously extrapolated to represent the broader fishery
- **Lineage**: Formatting, filtering
- **Keywords**: `r SPECIES_SELECTED`, IOTC species, catch, tuna fisheries
- **Type**: Tabular file
- **Format**: CSV
- **Size**: `r prettyNum(RC_BSE_DATA_SIZE, big.mark = ",")` KB for compressed dataset and `r prettyNum(RC_BSE_DATA_ZIP_SIZE, big.mark = ",")` KB for original dataset with code lists
- **Structures**: `r prettyNum(nrow(RC_BSE), big.mark = ",")` rows x `r prettyNum(ncol(RC_BSE), big.mark = ",")` columns
- **Taxonomic standard**: [ASFIS](https://data.apps.fao.org/catalog/dataset/cwp-asfis)
- **Geographic description**: Fishing areas within the Indian Ocean
- **Date standard**: [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601)
<!-- - **Data quality**: [IOTC reporting quality scoring](#RQS) -->
- **Update frequency**: At least twice per year
- **Metadata production date**: `r format(Sys.time(), '%d %B %Y')`
- **Source**: [IOTC](https://www.iotc.org/)
- **Contact**: [IOTC-Statistics@fao.org](mailto:IOTC-Statistics@fao.org)
- **Credit**: IOTC Secretariat
- **Associated rights**: Public-domain data requiring source acknowledgement

## Data processing {#processing}

## Dataset fields

```{r FieldsDefinitions}
datatable(FIELDS_RC_BSE_DATA_TABLE, escape = FALSE, rownames = FALSE, options = list(dom = 't', pageLength = nrow(FIELDS_RC_BSE_DATA_TABLE)))
```

## Data contents {#contents}

## Code lists

### Fleets

```{r FleetCodeList, eval = FALSE}
datatable(CL_FLEETS, rownames = FALSE, options = list(dom = 't', pageLength = nrow(CL_FLEETS)))
```

### Gears

```{r GearCodeList, eval = FALSE}
datatable(CL_GEARS, rownames = FALSE, options = list(dom = 't', pageLength = nrow(CL_GEARS)))
```
